### 2017-04-02 ThesisText/introduction.tex
Corrects typos

In the last few years E-Learning as been rising in popularity as a way to
deliver education and training in a remote setting. Institutions such as
universities and companies have been taking advantage of E-Learning in
different ways. Universities have been developing remote learning courses in
order to reach more people, and companies have been developing remote training
solutions to reach people in across different physical locations

This rise in popularity of E-Learning is due to the some factors. The
advancements of technology, such as the Internet, have not only contributed to
the development of better and more complex systems, but have also made possible
for those systems to reach more people and obtain grater adoption from users
and institutions.

These E-Learning platforms are called~\gls{lms}. The platforms
allow institutions not only to deliver training but also keep track of users,
courses, content, etc. In their normal operations, theses platforms generate
and store a lot of data. This data concerns the courses, the content in those
courses, activities from users, and so on. In some specific cases, like Moodle
in universities, the system may even keep track of the students grades.

The data becomes complex because these systems store a lot of information
regarding the users, courses, access logs, etc. Analysing this data, beyond
performing some statistical analysis, is not a trivial tasks. Some Data Mining
techniques may be apply to in order to make less trivial assumptions.

@@

Some statistical analysis are made to the preprocessed data repository before
any~\gls{dm} techniques are applied. This is done in order to to understand the
contents of the data and know which~\gls{dm} techniques should be applied and
to which subset of the data repository those techniques should be applied to.
Section~\ref{sec:stats} talks about these statistics and draws some conclusions
from them.

>>>>

In the last few years E-Learning has been rising in popularity as a way to
deliver education and training in a remote setting. Institutions such as
universities and companies have been taking advantage of E-Learning in
different ways. Universities have been developing remote learning courses in
order to reach more people, and companies have been developing remote training
solutions to reach people across different physical locations.

This rise in popularity of E-Learning is due to the some factors. The
advancements of technology, such as the Internet, have not only contributed to
the development of better and more complex systems, but have also made possible
for those systems to reach more people and obtain greater adoption from users
and institutions.

These E-Learning platforms are called~\gls{lms}. The platforms
allow institutions not only to deliver training but also keep track of users,
courses, content, etc. In their normal operations, theses platforms generate
and store a lot of data. This data concerns the courses, the content in those
courses, activities from users, and so on. In some specific cases, like Moodle
in universities, the system may even keep track of the student's grades.

The data becomes complex because these systems store a lot of information
regarding the users, courses, access logs, etc. Analysing this data, beyond
performing some statistical analysis, is not a trivial task. Some Data Mining
techniques may be applied in order to make less trivial assumptions.

@@

Some statistical analysis are made to the preprocessed data repository before
any~\gls{dm} techniques are applied. This is done in order to understand the
contents of the data and know which~\gls{dm} techniques should be applied and
to which subset of the data repository those techniques should be applied to.
Section~\ref{sec:stats} talks about these statistics and draws some conclusions
from them.

### 2017-04-02 ThesisText/statistics.tex
Corrects typos

Before applying any Data Mining methods, it is important to understand how the
data is constituted. Knowing things like, how many courses are there, how many
students, how many students per course, etc, is important in order to train
models and interpret the results.

@@

To begin exploring the courses, some counts are made. We count the number of
overall courses, the number of departments, and number of degrees.
Table~\ref{tab:courses_stats} shows these counts. We see 77 courses which are
part of 9 different departments and make up 11 degrees. While the number of
courses is much greater than some experiments mentioned in the background, it
is important to understand how many students does each of these courses have.

@@

It was to be expected that every degree would have a similar number of courses,
or at least that every course have curses for both semesters. It is unknown why
there are degrees present that have such characteristics, whether it is just
missing data or if there really are such degrees.

@@

Observing the behaviour of students in most courses in any University, it is
common to find that the number of students decreases over time has the course
progresses. This is due to students giving up on that course for that
particular semester for various reasons. Although the data doesn't have any
explicit data point stating that a student gave up on a course, we can still
observe student activity to verify if it decreases or not as the semester
progresses over the weeks.

@@

    \caption
        [Total number of active courses per week (bars) vs total active courses (Left)]
        {Total number of active courses per week (bars) vs total active courses (Left).}

>>>>

Before applying any Data Mining methods, it is important to understand how the
data is constituted. Knowing things like, how many courses there are, how many
students, how many students per course, etc, is important in order to train
models and interpret the results.

@@

To begin exploring the courses, some counts are made. We count the number of
overall courses, the number of departments, and number of degrees.
Table~\ref{tab:courses_stats} shows these counts. We see 77 courses which are
part of 9 different departments and make up 11 degrees. While the number of
courses is much greater than some experiments mentioned in the background, it
is important to understand how many students each of these courses have.

@@

It was to be expected that every degree would have a similar number of courses,
or at least that every degree has courses for both semesters. It is unknown why
there are degrees present that have such characteristics, whether it is just
missing data or if there really are such degrees.

@@

Observing the behaviour of students in most courses in any University, it is
common to find that the number of students decreases over time as the course
progresses. This is due to students giving up on that course for that
particular semester for various reasons. Although the data doesn't have any
explicit data point stating that a student gave up on a course, we can still
observe student activity to verify if it decreases or not as the semester
progresses over the weeks.

@@

    \caption
        [Total number of active courses per week (Bars) vs total active courses (Left)]
        {Total number of active courses per week (Bars) vs total active courses (Left).}
